### 2021-07-02 paper.tex
ref on susy+higher form sym

Our result is equally applicable in the case of \Nequals1 supersymmetric QCD, 
since they are connected to the non-supersymmetric QCD by a continuous deformation 
preserving all the symmetries we care about.
Now, let us recall that Intriligator and Seiberg found in \cite{Intriligator:1995id} a duality exchanging $\so(N_c)$ and $\so(N_f-N_c+4)$,
which in our notation sends $n_c$ to $n_c'=n_f-n_c+2$.
In \cite{Aharony:2013hda}, this duality was refined to account for the global form of the gauge group and the discrete theta angle, and it was concluded that $\Spin$ is exchanged with $\SO_-$ while $\SO_+$ maps to itself.
This mapping was given a further check e.g.~by using supersymmetric localization on $S^3/\bZ_n \times S^1$ in \cite{Razamat:2013opa}.
Our analysis allows us to check this duality by comparing how the 1-form symmetry and the 0-form symmetry are combined in the dual pairs.
We superimposed the action of the duality on our main Table~\ref{table:main}.
It is satisfying to see that the duality action correctly preserves the behaviors `none', `anomaly' and `extension'.

>>>>

Our result is equally applicable in the case of \Nequals1 supersymmetric QCD, 
since they are connected to the non-supersymmetric QCD by a continuous deformation 
preserving all the symmetries we care about.
Now, let us recall that Intriligator and Seiberg found in \cite{Intriligator:1995id} a duality exchanging $\so(N_c)$ and $\so(N_f-N_c+4)$,
which in our notation sends $n_c$ to $n_c'=n_f-n_c+2$.
In \cite{Aharony:2013hda}, this duality was refined to account for the global form of the gauge group and the discrete theta angle, and it was concluded that $\Spin$ is exchanged with $\SO_-$ while $\SO_+$ maps to itself.
This mapping was given a further check e.g.~by using supersymmetric localization on $S^3/\bZ_n \times S^1$ in \cite{Razamat:2013opa}.
Our analysis allows us to check this duality by comparing how the 1-form symmetry and the 0-form symmetry are combined in the dual pairs.
We superimposed the action of the duality on our main Table~\ref{table:main}.
It is satisfying to see that the duality action correctly preserves the behaviors `none', `anomaly' and `extension'.
In the last couple of years, the study of higher symmetries and their anomalies of supersymmetric theories has seen some activity\footnote{%
See e.g.~\cite{Tachikawa:2019dvq,Eckhard:2019jgg,Morrison:2020ool,Albertini:2020mdx,Apruzzi:2020zot,Cvetic:2020kuw,Gukov:2020btk,DelZotto:2020esg,DelZotto:2020sop,Bhardwaj:2020phs,Bhardwaj:2021pfz,Apruzzi:2021vcu,Cvetic:2021sxm,Apruzzi:2021phx,Bhardwaj:2021zrt,Buican:2021xhs,Braun:2021sex,Cvetic:2021maf}.},
but mostly from the point of view of string theory or M-theory.
The authors hope that this paper paves a way toward a more field-theoretical analysis of these matters.
